Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-05-24 src/tex/ms.tex
Beginning of forward model section and added important authors.

@@

\subsection{Designing a Bijection}
\label{sec:bijections}

@@

\subsubsection{Data Processing Bijections}
\label{sec:data-processing}

@@

\subsection{Choosing a Latent Distribution}

@@

\subsection{Conditional Flows}
\label{sec:conditional}

@@

\subsection{Flows with Periodic Topology}
\label{sec:periodic}

@@

The rest of this paper will demonstrate using PZFlow for the statistical modeling of galaxy catalogs.
Section \ref{sec:fwd-model} uses PZFlow to forward model a photometric catalog, including spectroscopic redshifts, Rubin photometry, ``true'' photo-z posteriors, ellipticities, and sizes.
Section \ref{sec:photo-z} uses PZFlow for photo-z estimation, demonstrating the power of PZFlow as a density estimator, including numerous useful features for photo-z estimation.

@@

>>>>

\author{J. Bryce Kalmbach}

\author{Alexander Gagliano}

\author{Alex Malz}

@@

\subsection{Designing a bijection}
\label{sec:bijections}

@@

\subsubsection{Data processing bijections}
\label{sec:data-processing}

@@

\subsection{Choosing a latent distribution}

@@

\subsection{Conditional flows}
\label{sec:conditional}

@@

\subsection{Flows with periodic topology}
\label{sec:periodic}

@@

The rest of this paper will demonstrate using PZFlow for the statistical modeling of galaxy catalogs.
Section \ref{sec:galaxy-catalog} uses PZFlow to forward model a photometric catalog, including spectroscopic redshifts, Rubin photometry, ``true'' photo-z posteriors, ellipticities, and sizes.
Section \ref{sec:photo-z} uses PZFlow for photo-z estimation, demonstrating the power of PZFlow as a density estimator, including numerous useful features for photo-z estimation.

@@

\section{Forward Modeling a Galaxy Catalog}
\label{sec:galaxy-catalog}

In this section, we apply PZFlow to forward model a photometric galaxy catalog for the Rubin Observatory.
The advantage of using a catalog generated from a normalizing flow is that we have direct access to the exact distribution from which the data is drawn, enabling us to calculate truth values for derived statistical products, such as the true photo-z redshift posterior for each galaxy.

In Section \ref{sec:fwd-model} we construct a normalizing flow to model the galaxy redshifts and photometry.
In Section \note{LABEL}, we calculate posteriors?
In Section \ref{sec:fwd-model-conditional} we build a conditional flow to add additional properties to the catalog.

\subsection{Forward modeling redshifts and photometry}
\label{sec:fwd-model}

\subsection{Calculating true posteriors}
\label{sec:true-posteriors}

\subsection{Additional properties with conditional flows}
\label{sec:fwd-model-condtional}

\section{Photometric Redshift Estimation}
\label{sec:photo-z}
